The Globular Cluster System of the Auriga Simulations

### 2019-04-28 AurigaGCS.tex
Added a paragraph to describe FeH distribution of Au4-24

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma}.png}
    \caption{
        First vs second central moment of the Auriga L4 metallicity distributions.
        Each dot represents one simulation for a given colour. The orange (blue) 
        [red] dots shows the values calculated using the old (old insitu) 
        [old accreted] star particles. Orange triangles indicate that all stars 
        were used. The purple (magenta) cross denotes our calculation using all 
        MW (M31) observations (i.e. asuming a unimodal distribution). The black 
        solid (open) dots indicate the literature values of a bimodal Gaussian 
        fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
        showing the the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}
Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the
[Fe/H] distribution of star particles in the Auriga L4 simulations. One dot 
of a given colour shows one particular simulation (thirty in total). The 
orange (blue) [red] dots represent the distributions of old (old insitu) 
[old accreted] star particles, and orange triangles indicate that all stars
were used. The mean metallicities of all GC candidates (orange dots) lie in the 
range $-0.95$ to $-0.4$, which is lower than when we include all star particles 
(orange triangles, centred around $\mu \sim 0$). Furthermore we find that the 
distributions of the accreted (insitu) GC candidates shift to slightly lower 
(higher) values and seem to be roughly centred around $\mu \sim -0.5$ ($-0.8$)
We find this trent that the distribution is more metal-poor (metal-rich)
when splitting the GC candidates into accreted (insitu) populations for the
majority of the Auriga simulations. The only exceptions are Au4-1 where this 
trent is reversed, and Au4-7 where all three (sub)populations have $\mu \sim -0.82$

>>>>

\begin{figure*}
    \includegraphics[width=\columnwidth]{{Au4-24_FeH_cleaner-trim}.png}
    \includegraphics[width=\columnwidth]{{Au4-24_FeH_mass-trim}.png}
    \caption{
        \emph{Left:} Metallicity distribution of Au4-24 (bottom panel). We show 
        the the GG candicates in orange. We split the GC candidates into two 
        subpopulations, those that have formed insitu (blue), and those that have 
        been accreted (red). The thin orange line shows all star particles.
        The solid purple (magenta) line in the top panel shows the GC system 
        of the MW (M31). \emph{Right:} Total mass in each metallicity bin.
        \label{fig:Au4-24_FeH}
    }
\end{figure*}
Figure~\ref{fig:Au4-24_FeH} shows the metallicity distribution of 
Au4-24\footnote{The nomenclature is `Au' for Auriga, followed by the resolution 
level (4) and halo number (24 - indicating which set of initial conditions was used 
the run).} as one particular example of an Auriga galaxy. The panel on the left
shows the distribution normalized by the number of particles, showing the GC
candidates in orange. The accreted GC candidates are shown in red, and the insitu
subpopulation is shown in blue. The top panel shows the MW (M31) GC system in
purple (magenta). We overplot two Gaussian curves (the purple dashed lines) using
literature values of the mean $\mu$ and standard deviation $\sigma$ of the 
metal-rich and metal-poor populations of the MW GCS \citep[][p. 38]{Harris2001}.
However, we use arbitrary normalizations to produce aesthetically pleasing curves.
The panel on the right shows the metallicity distribution weighted by the total
mass of the particles (observations) in that bin.

We find that the metallicity distribution of the Auriga simulations blabla.

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma}.png}
    \caption{
        First vs second central moment of the Auriga L4 metallicity distributions.
        Each dot represents one simulation for a given colour. The orange (blue) 
        [red] dots shows the values calculated using the old (old insitu) 
        [old accreted] star particles. Orange triangles indicate that all stars 
        were used. The purple (magenta) cross denotes our calculation using all 
        MW (M31) observations (i.e. asuming a unimodal distribution). The black 
        solid (open) dots indicate the literature values of a bimodal Gaussian 
        fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
        showing the the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the
[Fe/H] distribution of star particles in the Auriga L4 simulations. One dot 
of a given colour shows one particular simulation (thirty in total). The 
orange (blue) [red] dots represent the distributions of old (old insitu) 
[old accreted] star particles, and orange triangles indicate that all stars
were used. The mean metallicities of all GC candidates (orange dots) lie in the 
range $-0.95$ to $-0.4$, which is lower than when we include all star particles 
(orange triangles, centred around $\mu \sim 0$). Furthermore we find that the 
distributions of the accreted (insitu) GC candidates shift to slightly lower 
(higher) values and seem to be roughly centred around $\mu \sim -0.5$ ($-0.8$)
We find this trent that the distribution is more metal-poor (metal-rich)
when splitting the GC candidates into accreted (insitu) populations for the
majority of the Auriga simulations. The only exceptions are Au4-1 where this 
trent is reversed, and Au4-7 where all three (sub)populations have $\mu \sim -0.82$
